MCC Models

### 2020-09-22 papers/full_paper/Supplementary_information.Rmd
Update Supplementary_information.Rmd

As noted in the main text, the parameter $\alpha$ (speaker optimality parameter) in equation 2 determines the absolute strength of the likelihood term. Its interpretation is *how* rational $L_1$ thinks $S_1$ is in this particular context. For adults, we used the data from Experiment 1 to infer $\alpha$. That is, we performed a Bayesian analysis in which we used the integration model (assuming equal prior probability over referents), with an unknown a priori value of $\alpha$, and conditioned on the data from Experiment 1 to compute a posterior distribution over $\alpha$; in turn, the model generates posterior predictions for the proportion of correct responses in Experiment 1. We used MCMC to approximate the posterior distribution for $\alpha$ based on Experiment 1, computed the maximum a posteriori (MAP) and used this value for $\alpha$ to generate model predictions for Experiment 3 and 4.	The prior distribution was $\alpha \sim {\rm Cauchy }(1,2)$. We collected samples from four independent MCMC chains, collecting 6000 samples from each chain and removing the first 2000 for burn-in.

@@

The prior distribution over objects, $P(r)$, varied with the common ground manipulation, the identity of the speaker and the alignment of utterance and common ground information. Numerically, it depended on the measurement obtained in Experiment 2A and B for adults and Experiment 6 for children. Fig. \ref{fig:figS2} shows the test situation on Experiment 2.

For adults, this worked in the following way: For example, in Experiment 2, for the preference/same speaker condition, when the speaker previously indicated that they liked the yellow-ish object (right table in Fig. \ref{fig:figS2}) and disliked the pink-ish object (left table in Fig.\ref{fig:figS2}), the average proportion with which participants chose the yellow-ish object  was `r adult_ex2_preference_data %>% filter(condition == "same_speaker") %>% summarise(mean = mean(correct)) %>% pull(mean)` and for the pink-ish object it was `r 1-adult_ex2_preference_data %>% filter(condition == "same_speaker") %>% summarise(mean = mean(correct)) %>% pull(mean)` respectively. In Experiments 3 and 4, this measurement determined the prior distribution over objects in cases whenever the same manipulation was used (preference/same speaker). Note that Experiment 3 involved three objects while Experiment 2 only involved two. We nevertheless used the exact proportions measured in Experiment 2 for each object to inform the prior. This approach spread out the absolute probability mass but conserved the relative relation between objects. Thus, when utterance and common ground information were aligned (i.e. the yellow-ish object was the more informative object as in Fig. \ref{fig:figS1}), the distribution of objects was [$r_{p1}, r_{p2}, r_{y2}$]. Using the raw proportions, the corresponding prior distribution was [$P(r_{p}^1) = 0.03, P(r_{p}^2) = 0.03, P(r_{y}^2) = 0.97$] and after normalizing (so that they add up to 1) it was [0.03, 0.03, 0.94]. When information sources were dis-aligned (i.e. the pink-ish object was the more informative one), the object distribution was [$r_{y1}, r_{p2}, r_{y2}$] and the prior distribution was thus [0.97, 0.03, 0.97] or [0.49, 0.02, 0.49] after normalizing.

For children, we used the data from Experiment 6 to model the intercepts ($\beta^\rho_{0,j}$) and slopes ($\beta^\rho_{1,j}$) that best described the developmental trajectory in the data for each of the $j$ two conditions. As for the speaker optimality parameter, this allowed us to generate prior distributions that were sensitive to the child's age. We used a simple Bayesian logistic regression to find the intercept and slope (MAP of posterior distribution) that best described children's performance in the two conditions of experiment 6. The prior distribution was $\beta^\rho_0 ,\beta^\rho_1 \sim \text{Uniform}(-2,2)$ for the intercept and slope. We collected samples from four independent MCMC chains, collecting 6000 samples from each chain and removing the first 2000 for burn-in. In Experiment 7, the prior probability for an object was computed by taking the intercept for the respective condition ($j$), adding the slope times the child's age ($i$) and then using a logistic transformation to convert the outcome into proportions: $\rho_{i,j} = \text{logistic}(\beta^\rho_{0,j} + i \cdot \beta^\rho_{1,j})$. Because these proportions corresponded to a two object scenario they were then converted to the three object scenario via normalization in the same way as for adults. The overall distribution then depended on the alignment of information sources in the same way as it did for adults. Model code for inferring the intercept and the slope for the child study can be found in the associated online repository in the file `models.Rmd` starting line 1491.

>>>>

As noted in the main text, the parameter $\alpha$ (speaker optimality parameter) in equation 2 determines the absolute strength of the likelihood term. Its interpretation is *how* rational $L_1$ thinks $S_1$ is in this particular context. For adults, we used the data from Experiment 1 to infer $\alpha$. That is, we performed a Bayesian analysis in which we used the integration model (assuming equal prior probability over referents), with an unknown *a priori* value of $\alpha$, and conditioned on the data from Experiment 1 to compute a posterior distribution over $\alpha$; in turn, the model generates posterior predictions for the proportion of correct responses in Experiment 1. We used MCMC to approximate the posterior distribution for $\alpha$ based on Experiment 1, computed the *maximum a posteriori* (MAP) estimate and used this value for $\alpha$ to generate model predictions for Experiment 3 and 4.	The prior distribution was $\alpha \sim {\rm Cauchy }(1,2)$. We collected samples from four independent MCMC chains, collecting 6000 samples from each chain and removing the first 2000 for burn-in.

@@

The prior distribution over objects, $P(r)$, varied with the common ground manipulation, the identity of the speaker and the alignment of utterance and common ground information. Numerically, these probabilities depended on the measurement obtained in Experiment 2A and B for adults and Experiment 6 for children. Fig. \ref{fig:figS2} shows the test situation on Experiment 2.

For adults, the prior over objects was estimated in the following way: For example, in Experiment 2, for the preference/same speaker condition, when the speaker previously indicated that they liked the yellow-ish object (right table in Fig. \ref{fig:figS2}) and disliked the pink-ish object (left table in Fig.\ref{fig:figS2}), the average proportion with which participants chose the yellow-ish object  was `r adult_ex2_preference_data %>% filter(condition == "same_speaker") %>% summarise(mean = mean(correct)) %>% pull(mean)` and for the pink-ish object it was `r 1-adult_ex2_preference_data %>% filter(condition == "same_speaker") %>% summarise(mean = mean(correct)) %>% pull(mean)` respectively. In Experiments 3 and 4, this measurement determined the prior distribution over objects in cases whenever the same manipulation was used (preference/same speaker). Note that Experiment 3 involved three objects while Experiment 2 only involved two. We nevertheless used the exact proportions measured in Experiment 2 for each object as unnormalized probabilities in the prior. This approach  conserved the relative relation between object types. Thus, when utterance and common ground information were aligned (i.e. the yellow-ish object was the more informative object as in Fig. \ref{fig:figS1}), the distribution of objects was [$r_{p1}, r_{p2}, r_{y2}$]. Using the raw proportions, the corresponding prior distribution was [$P(r_{p}^1) = 0.03, P(r_{p}^2) = 0.03, P(r_{y}^2) = 0.97$] and after normalizing (so that they add up to 1) it was [0.03, 0.03, 0.94]. When information sources were dis-aligned (i.e. the pink-ish object was the more informative one), the object distribution was [$r_{y1}, r_{p2}, r_{y2}$] and the prior distribution was thus [0.97, 0.03, 0.97] or [0.49, 0.02, 0.49] after normalizing.

For children, we used the data from Experiment 6 to model the intercepts ($\beta^\rho_{0,j}$) and slopes ($\beta^\rho_{1,j}$) that best described the developmental trajectory in the data for each of the two ($j$) conditions. As for the speaker optimality parameter, this allowed us to generate object prior distributions in the cognitive model that were sensitive to the child's age. We used a simple Bayesian logistic regression to find the intercept and slope (MAP of posterior distribution) that best described children's performance in the two conditions of experiment 6. The prior distribution was $\beta^\rho_0 ,\beta^\rho_1 \sim \text{Uniform}(-2,2)$ for the intercept and slope. We collected samples from four independent MCMC chains, collecting 6000 samples from each chain and removing the first 2000 for burn-in. In Experiment 7, the prior probability for an object was computed by taking the intercept for the respective condition ($j$), adding the slope times the child's age ($i$) and then using a logistic transformation to convert the outcome into proportions: $\rho_{i,j} = \text{logistic}(\beta^\rho_{0,j} + i \cdot \beta^\rho_{1,j})$. Because these proportions corresponded to a two object scenario, they were then converted to the three object scenario via normalization in the same way as for adults. The overall distribution then depended on the alignment of information sources in the same way as it did for adults. Model code for inferring the intercept and the slope for the child study can be found in the associated online repository in the file `models.Rmd` starting line 1491.
